\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=0.5in]{geometry}

\title{CS685: Data Mining}
\author{Virendra Nishad (19111099)}
\date{}

\begin{document}

\maketitle
\vspace{5mm}
\section*{\underline{Report:}}
\vspace{5mm}
\begin{itemize}
    \item By observing only the name of the city which are on top list of two categories namely hot spot and cold spot. Few obvious conclusions about them are - \\
    \textbf{Districts in hot spot list:}
    \begin{itemize}
        \item All of them are popular economic cities, always used to be in news.
    \end{itemize}
    \textbf{Districts in cold spot list:}
    \begin{itemize}
        \item Almost all of them are very least heard type of cities.
    \end{itemize}
    
    Most of the districts which were in hot spot list in starting month are still in hot spot list. There is no variation in their status and this seems disturbing as it shows that number of confirmed cases in those districts are  continuously rising from almost seven months.
    
    \vspace{5mm}
    \item \textbf{Number of hot spot}
    \begin{itemize}
        \item There is very sharp rise in number of hot spot during the month March - May.
        \item Very slight dip in number of hot spot during the month of June.
        \item After that number of hot spot started to increase.
    \end{itemize}
    
    This is again a very sad sign. Almost one-sixth of the total district are in the list of hot spot. And since this list is increasing this shows that not only number of confirmed cases are growing across our country but also number of districts being badly affected by COVID19 are increasing.
    
    \vspace{5mm}
    \item \textbf{Number of cases per week}
    \begin{itemize}
        \item Few districts have started to show declination in number of confirmed cases .
        \item In some of the districts number of confirmed cases are continuously rising and
        \item In some districts rise in number of cases have started very recently.
    \end{itemize}
    
    There is variation in gaining peak among different cities and only in few cities number of confirmed cases have started to drop. Overall number of cases are still rising.
    
    \vspace{5mm}
    \item Some districts which were in cold spot list are now in hot spot list and some of them were added very recently in this list like tripura, patna etc and it seems that there is only shift of hot spot but no declination in confirmed cases count.
    
    \vspace{5mm}
    \item This means that peak is not over yet and if cases in these newly districts will continue to rise, then we have to prepare for long battle against this disease as this disease does not seems to end soon by it's own.
    
\end{itemize}

\end{document}
